### 2015-02-22 fundamentals/fcsreqs.tex
fixed ie/eg

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
platform on which it relies is often restricted or costly.  However, \Cyclus
provides fully free and open access to all users
and developers, foreign and domestic.

@@

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
\gls{VISION}) are unable to capture this gracefully, perhaps representing it as 
a reduction in the capacity of the whole fleet.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
The \Cyclus framework does not dictate such heuristics. Rather, it provides a
flexible framework on which either method is possible.

>>>>

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (e.g. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
the source code is unrestricted, the platform on which it relies is often
restricted or costly.  However, \Cyclus provides fully free and open access to
all users and developers, foreign and domestic.

@@

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (e.g.
\gls{VISION}) are unable to capture this gracefully, perhaps representing it as
a reduction in the capacity of the whole fleet.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
The \Cyclus framework does not dictate such heuristics. Rather, it provides a
flexible framework on which either method is possible.
